---
title: "Ch12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
```
## Ch 12

## 12.2.1
1. variables are in the vertical columns, observations are in the horizontal rows, and values are in each of the cells.
```
mutate(rate = cases/population * 1000)
```
3. library(ggplot2)
  ggplot(table 2, aes(year, type)) +
  geom_line(aes(group = country), color = "grey50")+
  geom_point(aes(color = country))
  
## 12.3.3
1. they are not perfectly symmetrical because collumns are being combined or seperated 
2. the code fails because they didn't put the years in quotes. the years 1999 and 2000 are variables not numeric values
3. if you were to widen the table your collumns would be name, age, and height
it could be longer by changing it to pregnant , sex, age

## 12.4.3
1. extra will drop any extra values
  fill will fill gaps with values on the right
2. remove will remove an input column from output data frame


## 12.5.1
1. they both have list of values to be used in place of any missing values. pivot_wider says it is optional and complete is specifically replacing NA
2.

## 12.6.1
1. 
